Consistent Polyhedral Surrogates via Embedding

### 2019-05-20 notes/jessie-proof-sketches.tex
comments on prop 1

  \jessie{Redone.  Original version in comments below.}
  For the forward implication, suppose $L$ embeds the discrete loss $\ell$ via the embedding $\varphi$.
  Then $\Gamma := \prop{L}$ embeds the finite property $\gamma:\simplex \toto \R$ elicited by $\ell$.
  Call $\R' := \varphi(\R)$.
  For all $p \in \simplex$, we know that $\Gamma(p) = \varphi(\gamma(p))$.
  We know $\gamma' := \Gamma(p) \cap \R'$ is nonempty for all $p \in \simplex$ since $\Gamma(p) = \varphi(\gamma(p)) \subseteq \R'$.
  By \jessie{COLT Lemma 11}, we know that $L|_{\R'}$ elicits $\gamma'$ and $\risk{L} = \risk{L|_{\R'}}$.

@@

  To start, assume that $\risk{L} = \risk{\ell}$.
  The projection of the epigraphs onto $\simplex$ must then form the same power diagram \jessie{COLT Theorem 33}, corresponding to the level sets of the properties each loss elicits.
  Notably, \jessie{as in proof of COLT Prop 12,} the facets of $\risk{\ell}$ project onto the level sets of $\gamma := \prop{\ell}$.
  As $\ell$ is discrete, we know $\gamma$ is finite, and so the level sets of $\gamma$ are full-dimensional \jessie{by COLT Lemma 10} and union to the simplex by nondegeneracy of $\gamma$.
  Since the risks of $L$ and $\ell$ are the same (and therefore, so are their projections onto $\simplex$), this same [finite] subset $\Theta$ of the level sets of $\Gamma$ that union to the simplex and are full-dimensional.
  By \jessie{COLT Prop 12}, we can then conclude that $\Gamma$ embeds the finite property $\gamma$, and thus $L$ embeds the discrete loss $\ell$.

>>>>

  \jessie{Redone.  Original version in comments below.}
  For the forward implication, suppose $L$ embeds the discrete loss $\ell$ via the embedding $\varphi$.
  Then $\Gamma := \prop{L}$ embeds the finite property $\gamma:\simplex \toto \R$ elicited by $\ell$.
  Call $\R' := \varphi(\R)$.
  For all $p \in \simplex$, we know that $\Gamma(p) = \varphi(\gamma(p))$ \raf{Not true; focus on the next statement and show directly using def of embedding}.
  We know $\gamma' := \Gamma(p) \cap \R'$ is nonempty for all $p \in \simplex$ since $\Gamma(p) = \varphi(\gamma(p)) \subseteq \R'$.
  By \jessie{COLT Lemma 11}, we know that $L|_{\R'}$ elicits $\gamma'$ and $\risk{L} = \risk{L|_{\R'}}$.

@@

  To start, assume that $\risk{L} = \risk{\ell}$.
  The projection of the epigraphs onto $\simplex$ must then form the same power diagram \jessie{COLT Theorem 33}, corresponding to the level sets of the properties each loss elicits.
  Notably, \jessie{as in proof of COLT Prop 12,} the facets of $\risk{\ell}$ project onto the level sets of $\gamma := \prop{\ell}$.
  As $\ell$ is discrete, we know $\gamma$ is finite \raf{note for later: we have to be careful about ``discrete'' and ``finite'' since they both bake in regularity conditions, like nondegeneracy as you mention, but also non-redundancy}, and so the level sets of $\gamma$ are full-dimensional \jessie{by COLT Lemma 10} and union to the simplex by nondegeneracy of $\gamma$.
  Since the risks of $L$ and $\ell$ are the same (and therefore, so are their projections onto $\simplex$), this same [finite] subset $\Theta$ of the level sets of $\Gamma$ that union to the simplex and are full-dimensional.
  By \jessie{COLT Prop 12}, we can then conclude that $\Gamma$ embeds the finite property $\gamma$, \raf{wait, you skipped the other condition for losses embedding each other $\rightarrow$} and thus $L$ embeds the discrete loss $\ell$.
